THESIS TITLE

### 2023-09-18 subsections/simulation/intermediate_versions/intermediate.tex
push for sina1

Addition of bunches would immediately proven useful when finding optimal phase lag for bunch entry.
$\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch has entered the cavity and it defines the starting time of the current pass.
To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
\begin{itemize}
    \item $\mu E$: Average energy
    \item $E_{rms}$: Root mean square of energy
    \item $R_{rms}$: Root mean square of \e positions
\end{itemize}
Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, initial implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}). 
For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as \textit{ROOT framework}. 
\begin{figure}[H]
    \centering
    \captionsetup{justification=centering}
    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
        int phase_opt(int phase_sweep_range){
            double minrms = 1;
            int opt_phase;
            for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
              Bunch bunch1(RFphase);
              double t1 = 0;
              bunch1.bunch_gecis_t(t1);
              bunch1.reset_pos();

              if( bunch1.E_rms() < minrms ){
                minrms = bunch1.E_rms();
                opt_phase = RFphase;
              }
            }
            return opt_phase;
        }
    \end{minted}
    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
    \label{fig:phlag_opt}
\end{figure}
Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}). 
This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.

@@

Interaction logic for \eE and \eB in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \begin{subfigure}{\textwidth}
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
            vector3d CoaxialRFField::actOn(Electron& e){
                vector3d Efield = getField(e.pos);                          // Calculate E vector
                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
                return acc;
            }
        \end{minted}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
            vector3d MagneticField::actOn(Electron& e){
                if (isInside(e.pos) == -1)
                    return vector3d(0,0,0);
                vector3d Bfield = getField(e.pos);                          // Calculate B vector
                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
                return acc;
            }
        \end{minted}
    \end{subfigure}
    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}}
    \label{fig:3D_e_EM_interaction_first}
\end{figure}
Where * and \% are, dot-product and cross-product respectably. (\fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})

Simulating in 3D had one other benefit; it was now possible to visualize the results by rendering the interaction data. 
For this purpose, \textit{gnuplot} was integrated into \textit{Rhodotron Simulation} to produce 2D visualization of acceleration plane. 
Rendered results could be stored as \textit{gif} animations. 
Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{0.9\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/5ns_gnuplot.png}
        \caption*{Unsyncronized \e gun period, $T_g = 5ns$}
    \end{subfigure}
    \begin{subfigure}{0.9\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/9_3ns_gnuplot.png}
        \caption*{Syncronized \e gun period, $T_g = 9.3ns$}
    \end{subfigure}
    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}\\$P=12$kW, $f=107.5$MHz}
    \label{fig:example_gnuplot_renders}
\end{figure}

\subsection{Acceleration in Magnetic Field}
An issue regarding the \eB interaction became apparent when energy gain during these interactions was observed.
A setup simulation was implemented in which a bunch of 100\e at $1$MeV was fired into a uniform magnetic field of $0.1$T located in $x>0.05$m.
Initial results at $dt=0.01$ns proved the suspicion of \eB interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
\begin{figure}
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/mag_lf_001dt.png}
        \caption*{$dt=10^{-2}$ns, $\Delta E=2.783$MeV}
    \end{subfigure}
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/mag_lf_00001dt.png}
        \caption*{$dt=10^{-4}$ns, $\Delta E=0.011$MeV}
    \end{subfigure}
    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T}
    \label{fig:mag_lf_render}
\end{figure}
Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable due to computing power limitations. 
Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for \eEM interactions. 
To test newer approaches, two additional version of  \eEM interaction that are using \fromsec{rungekutta} were added.
\subsubsection{RK4-1}
First approach for integrating \fromsec{rungekutta} into \eEM interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using \textit{RK4}.
After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, \e would move and accelerate using the \textit{Leap-frog} method. 
The idea was to produce more refined interaction results, leading to improved accuracy especially in \eB.
RF field was kept static during the RK4 computation, due to ongoing \textit{multithreading} implementation efforts. 
The implementation can be found in \fromfigs{rk1_B}{rk1_EM}.
\subsubsection{RK4-2}
Following the implementation of \textit{RK4-1}, revisions were made to the integration method for \textit{RK4} to replace \textit{Leap-frog}.
Instead of calculating $\vecthreeBF{a}_{EM}$ using \textit{RK4}, $\vecthreeBF{r}$ and $\vecthreeBF{v}$ would be determined directly.

@@

More rigerous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
\begin{figure}
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/analiz/mag_lf_rk2_dt-E.png}
        \caption*{$dt$ vs $\Delta E$}
    \end{subfigure}

    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/analiz/mag_lf_rk2_dt-Tsim.png}
        \caption*{$dt$ vs $T_{sim}$}
    \end{subfigure}
    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
    \label{fig:mag_lf_rk2_comparison}
\end{figure}
The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
To investigate the data further, one can define a performance measurement, $F$.
\begin{eqnarray*}
    F &\propto& 1/T \\
    F &\propto& 1/\Delta E 
\end{eqnarray*}
When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity,
\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
    \Delta E_{LF} &=& 110 \times 10^{-5} MeV \nonumber\\
    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV \nonumber\\
    T_{LF}^1 &=& 9.44 \pm 0.03 s \nonumber\\
    T_{RK}^1 &=& 21.33 \pm 0.02 s \nonumber\\
    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s \nonumber\\ %0.003
    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s \nonumber\\ %0.001
    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01
\end{eqnarray}
Also, observing from the data,
\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV \nonumber\\
    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s \nonumber\\ %0.0032
    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s \nonumber\\ %0.0022
    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1
\end{eqnarray}
Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
\begin{equation}
    F_{LF}/F_{RK} = 1.36 \pm 0.05
\end{equation}
Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
\textit{RK4} was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
\textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.

@@

As test setups, two simulation confgurations were made. They aimed to test the accuracy of acceleration of a beam in parallel and perpendicular static uniform electric fields.
Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV. 
\begin{figure}[H]
    \centering
    \begin{subfigure}{0.47\textwidth}
        \centering
        \includegraphics[width=0.9\linewidth]{../../../figures/illustrations/statE_1.png}
        \caption*{Setup-1 parallel $\vecthreeBF{E}$ field}
    \end{subfigure}
    \begin{subfigure}{0.48\textwidth}
        \centering
        \includegraphics[width=0.9\linewidth]{../../../figures/illustrations/statE_2.png}
        \caption*{Setup-2, perpendicular $\vecthreeBF{E}$ field}
    \end{subfigure}
    \caption{Illustration of test setups.}
\end{figure}
In the first test, the beam would be injected into a static uniform electric field \\
$\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.

Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753}{0}{0}m is
\begin{eqnarray}
    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \\
             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \\
             &=& 2.65616 \times 1.506 \\
    \Delta V^1 &=& 4 MV \\
    \Delta E^1 &=& 4 MeV \\
    E_{exitTH}^1 &=& 5 MeV
\end{eqnarray}
In the second test on the other hand, the beam would be injected into a different static uniform electric field, \\
$\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
\begin{eqnarray}
    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \\
                 &=& - \int_{0}^{0.753} -5.31232 \times dy \\
                 &=& 5.31232 \times 0.753 \\
    \Delta V^2   &=& 4 MV \\
    \Delta E^2   &=& 4 MeV \\
    E_{exitTH}^2 &=& 5 MeV
\end{eqnarray}
Therefore, in the both tests, the beam was expected to exit $\vecthreeBF{E}$ with $E_{exitTH} = 5$ MeV. 
To also measure the variance in simulation completion times, $T_{sim}$, set of $10$ runs were completed at the configuration for each $dt$ value.
Results from these tests can be observed in \fromfig{lf_rk2_perp_stat_E_comparison} and \fromfig{lf_rk2_par_stat_E_comparison} of \fromapp{data_graph}.
\begin{figure}[H]
    \centering
    \begin{subfigure}{0.9\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/statE_par.png}
        \caption*{Setup-1, $\textbf{V}_{\parallel}$=4MV}
    \end{subfigure}
    \begin{subfigure}{0.9\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/statE_perp.png}
        \caption*{Setup-2, $\textbf{V}_{\perp}$=4MV}
    \end{subfigure}
    \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ns}
\end{figure}

\begin{figure}[H]
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{0.9\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/analiz/90staticE_lf_rk2_dt-E_3.png}
    \end{subfigure}

>>>>

Addition of bunches would immediately proven useful when finding optimal phase lag for bunch entry.
$\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch has entered the cavity and it defines the starting time of the current pass.
To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as
\begin{itemize}
    \item $\mu E$: Average energy,
    \item $E_{rms}$: Root mean square of energy,
    \item $R_{rms}$: Root mean square of \e positions.
\end{itemize}
Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, initial implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}). 
For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as \textit{ROOT framework}. 
\begin{figure}[H]
    \centering
    %\captionsetup{justification=centering}
    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
        int phase_opt(int phase_sweep_range){
            double minrms = 1;
            int opt_phase;
            for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
              Bunch bunch1(RFphase);
              double t1 = 0;
              bunch1.bunch_gecis_t(t1);
              bunch1.reset_pos();

              if( bunch1.E_rms() < minrms ){
                minrms = bunch1.E_rms();
                opt_phase = RFphase;
              }
            }
            return opt_phase;
        }
    \end{minted}
    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design.}
    \label{fig:phlag_opt}
\end{figure}
Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}). 
This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.

@@

Interaction logic for \eE and \eB in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
\iffalse \begin{figure}[H]
    %\captionsetup[subfigure]{justification=centering}
    %\captionsetup{justification=centering}
    \begin{subfigure}{\textwidth}
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
            vector3d CoaxialRFField::actOn(Electron& e){
                vector3d Efield = getField(e.pos);                          // Calculate E vector
                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
                return acc;
            }
        \end{minted}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
            vector3d MagneticField::actOn(Electron& e){
                if (isInside(e.pos) == -1)
                    return vector3d(0,0,0);
                vector3d Bfield = getField(e.pos);                          // Calculate B vector
                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
                return acc;
            }
        \end{minted}
    \end{subfigure}
    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}.}
    \label{fig:3D_e_EM_interaction_first}
\end{figure} \fi
\begin{figure}[H]
    %%\captionsetup[subfigure]{justification=centering}
    %%\captionsetup{justification=centering}
    \begin{minipage}{\textwidth}
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
            vector3d CoaxialRFField::actOn(Electron& e){
                vector3d Efield = getField(e.pos);                          // Calculate E vector
                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
                return acc;
            }
        \end{minted}
    \end{minipage}

    \begin{minipage}{\textwidth}
        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
            vector3d MagneticField::actOn(Electron& e){
                if (isInside(e.pos) == -1)
                    return vector3d(0,0,0);
                vector3d Bfield = getField(e.pos);                          // Calculate B vector
                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
                return acc;
            }
        \end{minted}
    \end{minipage}
    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}.}
    \label{fig:3D_e_EM_interaction_first}
\end{figure}
Where * and \% are, dot-product and cross-product respectably. (\fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})

Simulating in 3D had one other benefit; it was now possible to visualize the results by rendering the interaction data. 
For this purpose, \textit{gnuplot} was integrated into \textit{Rhodotron Simulation} to produce 2D visualization of acceleration plane. 
Rendered results could be stored as \textit{gif} animations. 
Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
\iffalse \begin{figure}[H]
    %\captionsetup[subfigure]{justification=centering}
    %\captionsetup{justification=centering}
    \centering
    \begin{subfigure}{0.9\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/5ns_gnuplot.png}
        \caption*{Unsyncronized \e gun period, $T_g = 5ns$}
    \end{subfigure}
    \begin{subfigure}{0.9\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/9_3ns_gnuplot.png}
        \caption*{Syncronized \e gun period, $T_g = 9.3ns$}
    \end{subfigure}
    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation} $P=40$kW, $f=107.5$MHz.}
    \label{fig:example_gnuplot_renders}
\end{figure} \fi
\begin{figure}[H]
    \centering
    \subfigure[\centering Unsyncronized \e gun period, $T_g = 5ns$]{{\includegraphics[width=0.85\textwidth]{../../../figures/rhodoSim/5ns_gnuplot.png}}}%
    \vspace{15pt}
    \centering
    \subfigure[\centering Syncronized \e gun period, $T_g = 9.3ns$]{{\includegraphics[width=0.85\textwidth]{../../../figures/rhodoSim/9_3ns_gnuplot.png}}}%
    \vspace{15pt}
    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}, $P=40$kW, $f=107.5$MHz.} 
    \label{fig:example_gnuplot_renders}
\end{figure}

\subsection{Acceleration in Magnetic Field}
An issue regarding the \eB interaction became apparent when energy gain during these interactions was observed.
A setup simulation was implemented in which a bunch of 100\e at $1$MeV was fired into a uniform magnetic field of $0.1$T located in $x>0.05$m.
Initial results at $dt=0.01$ns proved the suspicion of \eB interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
\iffalse \begin{figure}
    %\captionsetup[subfigure]{justification=centering}
    %\captionsetup{justification=centering}
    \centering
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/mag_lf_001dt.png}
        \caption*{$dt=10^{-2}$ns, $\Delta E=2.783$MeV}
    \end{subfigure}
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/mag_lf_00001dt.png}
        \caption*{$dt=10^{-4}$ns, $\Delta E=0.011$MeV}
    \end{subfigure}
    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T}
    \label{fig:mag_lf_render}
\end{figure} \fi
\begin{figure}
    \centering
    \subfigure[\centering $dt=10^{-2}$ns, $\Delta E=2.783$MeV]{{\includegraphics[width=0.8\textwidth]{../../../figures/rhodoSim/mag_lf_001dt.png} }}%
    \vspace{15pt}
    \subfigure[\centering $dt=10^{-4}$ns, $\Delta E=0.011$MeV]{{\includegraphics[width=0.8\textwidth]{../../../figures/rhodoSim/mag_lf_00001dt.png} }}%
    \vspace{15pt}
    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T.}
    \label{fig:mag_lf_render}
\end{figure}
Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable due to computing power limitations. 
Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for \eEM interactions. 
To test newer approaches, two additional version of  \eEM interaction that are using \fromsec{rungekutta} were added.
\subsubsection{RK4-1}
First approach for integrating \fromsec{rungekutta} into \eEM interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using \textit{RK4}.
After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, \e would move and accelerate using the \textit{Leap-frog} method. 
The idea was to produce more refined interaction results, leading to improved accuracy especially in \eB.
RF field was kept static during the RK4 computation, due to ongoing \textit{multithreading} implementation efforts. 
The implementation can be found in \fromfigs{rk1_B}{rk1_EM}.
\subsubsection{RK4-2}
Following the implementation of \textit{RK4-1}, revisions were made to the integration method for \textit{RK4} to replace \textit{Leap-frog}.
Instead of calculating $\vecthreeBF{a}_{EM}$ using \textit{RK4}, $\vecthreeBF{r}$ and $\vecthreeBF{v}$ would be determined directly.

@@

More rigerous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
\iffalse \begin{figure}
    %\captionsetup[subfigure]{justification=centering}
    %\captionsetup{justification=centering}
    \centering
    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/analiz/mag_lf_rk2_dt-E.png}
        \caption*{$dt$ vs $\Delta E$}
    \end{subfigure}

    \begin{subfigure}{0.8\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/analiz/mag_lf_rk2_dt-Tsim.png}
        \caption*{$dt$ vs $T_{sim}$}
    \end{subfigure}
    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
    \label{fig:mag_lf_rk2_comparison}
\end{figure} \fi
\begin{figure}
    \centering
    \subfigure[\centering $dt$ vs $\Delta E$]{{\includegraphics[width=0.8\textwidth]{../../../figures/analiz/mag_lf_rk2_dt-E.png} }}%
    \qquad\subfigure[\centering $dt$ vs $T_{sim}$]{{\includegraphics[width=0.8\textwidth]{../../../figures/analiz/mag_lf_rk2_dt-Tsim.png} }}%
    \vspace{20pt}
    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns.}
    \label{fig:mag_lf_rk2_comparison}
\end{figure}
The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
To investigate the data further, one can define a performance measurement, $F$ as
\vspace{-10pt}\begin{eqnarray*}
    F &\propto& 1/T  , \\
    F &\propto& 1/\Delta E . 
\vspace{-10pt}\end{eqnarray*}
When $dt=10^{-5}$ ns was taken as reference point due to providing a good balance of accuracy and computational intensity, 
relative performance can be calculated as
\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
    \Delta E_{LF} &=& 110 \times 10^{-5} MeV,\nonumber\\
    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV,\nonumber\\
    T_{LF}^1 &=& 9.44 \pm 0.03 s, \nonumber\\
    T_{RK}^1 &=& 21.33 \pm 0.02 s, \nonumber\\
    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s, \nonumber\\ %0.003
    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s, \nonumber\\ %0.001
    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01 .
\vspace{-10pt}\end{eqnarray}
Also, another relative performance can be obsered from the data as
\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV, \nonumber\\
    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s, \nonumber\\ %0.0032
    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s, \nonumber\\ %0.0022
    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1.
\vspace{-10pt}\end{eqnarray}
Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. 
After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
\vspace{-10pt}\begin{equation}
    F_{LF}/F_{RK} = 1.36 \pm 0.05.
\vspace{-10pt}\end{equation}
Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
\textit{RK4} was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
\textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.

@@

As test setups, two simulation confgurations were made. They aimed to test the accuracy of acceleration of a beam in parallel and perpendicular static uniform electric fields.
Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV. 
\iffalse \begin{figure}[H]
    \centering
    \begin{subfigure}{0.47\textwidth}
        \centering
        \includegraphics[width=0.9\linewidth]{../../../figures/illustrations/statE_1.png}
        \caption*{Setup-1 parallel $\vecthreeBF{E}$ field}
    \end{subfigure}
    \begin{subfigure}{0.48\textwidth}
        \centering
        \includegraphics[width=0.9\linewidth]{../../../figures/illustrations/statE_2.png}
        \caption*{Setup-2, perpendicular $\vecthreeBF{E}$ field}
    \end{subfigure}
    \caption{Illustration of test setups.}
\end{figure} \fi
\begin{figure}[H]
    \centering
    \subfigure[\centering Setup-1 parallel $\vecthreeBF{E}$ field]{{\includegraphics[width=0.423\textwidth]{../../../figures/illustrations/statE_1.png} }}%
    \qquad\subfigure[\centering Setup-2, perpendicular $\vecthreeBF{E}$ field]{{\includegraphics[width=0.432\textwidth]{../../../figures/illustrations/statE_2.png} }}%
    \vspace{20pt}
    \caption{Illustration of test setups.}
\end{figure}
In the first test, the beam would be injected into a static uniform electric field \\
$\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.

Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753}{0}{0}m is
\vspace{-10pt}\begin{eqnarray}
    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \\
             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \\
             &=& 2.65616 \times 1.506 \\
             &=& 4 MV, \\
    \Delta E^1 &=& 4 MeV, \\
    E_{exitTH}^1 &=& 5 MeV.
\vspace{-10pt}\end{eqnarray}

In the second test on the other hand, the beam would be injected into a different static uniform electric field,
$\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
\vspace{-10pt}\begin{eqnarray}
    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \\
                 &=& - \int_{0}^{0.753} -5.31232 \times dy \\
                 &=& 5.31232 \times 0.753 \\
                 &=& 4 MV, \\
    \Delta E^2   &=& 4 MeV, \\
    E_{exitTH}^2 &=& 5 MeV.
\vspace{-10pt}\end{eqnarray}

Therefore, in the both tests, the beam was expected to exit $\vecthreeBF{E}$ with $E_{exitTH} = 5$ MeV. 
To also measure the variance in simulation completion times, $T_{sim}$, set of $10$ runs were completed at the configuration for each $dt$ value.
Results from these tests can be observed in \fromfig{lf_rk2_perp_stat_E_comparison} and \fromfig{lf_rk2_par_stat_E_comparison} of \fromapp{data_graph}.
\iffalse \begin{figure}[H]
    \centering
    \begin{subfigure}{0.9\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/statE_par.png}
        \caption*{Setup-1, $\textbf{V}_{\parallel}$=4MV}
    \end{subfigure}
    \begin{subfigure}{0.9\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/statE_perp.png}
        \caption*{Setup-2, $\textbf{V}_{\perp}$=4MV}
    \end{subfigure}
    \caption{Render of the test setups.  $E_{in}=1$ MeV, $t_{end}=6$ ns}
\end{figure} \fi
\begin{figure}[H]
    \centering
    \subfigure[\centering Setup-1, $\textbf{V}_{\parallel}$=4MV]{{\includegraphics[width=0.85\textwidth]{../../../figures/rhodoSim/statE_par.png} }}%
    \vspace{15pt}
    \subfigure[\centering Setup-2, $\textbf{V}_{\perp}$=4MV]{{\includegraphics[width=0.85\textwidth]{../../../figures/rhodoSim/statE_perp.png} }}%
    \vspace{15pt}
    \caption{Render of the test setups.  $E_{in}=1$ MeV, $t_{end}=6$ ns.}
\end{figure}
